Geometric variational problems

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
starting fluctuating hydro

\begin{wrapfigure}[21]{r}{3.0in}
%\vspace*{+15pt}
\centerline{\includegraphics[width=3.0in]{figures/integrands}}
\vspace*{-10pt}
\caption{{\footnotesize The Fourier modes of $K(x_0,y)$ and $K_2(x_0,y)$
  where $|x_0| = 0.99$ and $\partial\Omega$ is the unit circle. The
  trapezoid rule applied to the red integrand has large amounts of
  error. However, the trapezoid rule is much more accurate when applied
  to the blue integrand. Since the difference between the red and blue
  curves can be accurately computed with the barycentric quadrature
  rule, the error of this quadrature rule applied to the screened
  Laplace layer potential will be uniformly bounded in $\Omega$.}}
\label{fig:integrands}
\end{wrapfigure}
Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
particles, and such near-contact results in nearly-singular integrands
in both two and three dimensions. Quadrature methods to address such
integrands has received a lot of attention in two and three
dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2, davis_1984,
graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003, khayat_2005,
schwab_1992, ying_2006, beale1, beale2, goodman_1990, haroldson_1998,
lowengrub_1993, schwab_1992, ggq1, ggq2, ggq3, helsing_2008a,
helsing_integral_2009, helsing_tutorial_2012, klockner2013jcp, qbx2,
wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
bar2014}. For two-dimensional problems, the trapezoid rule is the
workhorse for BIEs since it achieves spectral accuracy when integrands
are not nearly-singular~\cite{tre-wei2014}. To address nearly-singular
integrands of two dimensional BIEs, we will use a {\em barycentric
quadrature rule} that only requires a slight modification of the
trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
requires the layer potential satisfy Laplace or Stokes
equations~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs will extend
this quadrature rule so that it can be applied to the screened Laplace
equation. This will be done by recognizing that the fundamental solution
of the screened Laplace equation can be decomposed as $K(x,y) = K_1(x,y)
+ K_2(x,y)$, where $K_1(x,y) = -\log\|x - y\|$ and $K_2(x,y) = K(x,y) +
\log\|x - y\|$. Using this decomposition, the layer potential involving
$K_1(x,y)$ can be accurately computed with the barycentric quadrature
rule~\cite{ioa-pap-per1991}, and the layer potential $K_2(x,y)$ can be
accurately computed with the trapezoid rule since the kernel is bounded
for all $x$ and $y$. To proposed method is demonstrated in
Figure~\ref{fig:integrands} where the amplitude of the Fourier modes of
$K(x_0,y)$ and $K_2(x_0,y)$ are plotted. The quadrature of the trapezoid
rule is the sum of the Fourier amplitudes not captured at the
resolution.

@@

% ----------------------------------------------------------------------
\subsubsection{Fluctuating hydrodynamics}
\label{subsec:fluctuating}
Using DLP formulation for fluctuating hydrodynamics so that we have a
second-kind BIE
\textcolor{red}{
Once the collision-resolution algorithm is implemented, we will check
the computing performance first before we embark on incorporating
fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
even at the scales of the amphiphilic particle size in some cases. We
propose to extend the high-order time-integration scheme for a
stochastic differential equation~\cite{fu2015pre} to this system.
}

>>>>

\begin{wrapfigure}[21]{r}{3.0in}
%\vspace*{+15pt}
\centerline{\includegraphics[width=3.0in]{figures/integrands}}
\vspace*{-10pt}
\caption{{\footnotesize The Fourier modes of $K(x_0,y)$ and $K_2(x_0,y)$
  where $\|x_0\| = 0.99$ and $\partial\Omega$ is the unit circle. The
  trapezoid rule applied to the red integrand has large amounts of
  error. However, the trapezoid rule is much more accurate when applied
  to the blue integrand. Since the difference between the red and blue
  curves can be accurately computed with the barycentric quadrature
  rule, the error of this quadrature rule applied to the screened
  Laplace layer potential will be uniformly bounded in $\Omega$.}}
\label{fig:integrands}
\end{wrapfigure}
Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
particles, and such near-contact results in nearly-singular integrands
in both two and three dimensions. Quadrature methods to address such
integrands has received a lot of attention in two and three
dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2, davis_1984,
graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003, khayat_2005,
schwab_1992, ying_2006, beale1, beale2, goodman_1990, haroldson_1998,
lowengrub_1993, schwab_1992, ggq1, ggq2, ggq3, helsing_2008a,
helsing_integral_2009, helsing_tutorial_2012, klockner2013jcp, qbx2,
wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
bar2014}. For two-dimensional problems, the trapezoid rule is the
workhorse for BIEs since it achieves spectral accuracy when integrands
are not nearly-singular~\cite{tre-wei2014}. To address nearly-singular
integrands of two dimensional BIEs, we will use a {\em barycentric
quadrature rule} that only requires a slight modification of the
trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
requires the layer potential satisfy Laplace or Stokes
equations~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs will extend
this quadrature rule so that it can be applied to the screened Laplace
equation. This will be done by recognizing that the fundamental solution
of the screened Laplace equation can be decomposed as $K(x,y) = K_1(x,y)
+ K_2(x,y)$, where $K_1(x,y) = -\log\|x - y\|$ and $K_2(x,y) = K(x,y) +
\log\|x - y\|$. Using this decomposition, the layer potential involving
$K_1(x,y)$ can be accurately computed with the barycentric quadrature
rule~\cite{ioa-pap-per1991}, and the layer potential $K_2(x,y)$ can be
accurately computed with the trapezoid rule since the kernel is bounded
for all $x$ and $y$. To proposed method is demonstrated in
Figure~\ref{fig:integrands} where the amplitude of the Fourier modes of
$K(x_0,y)$ and $K_2(x_0,y)$ are plotted. The quadrature of the trapezoid
rule is the sum of the Fourier amplitudes not captured at the
resolution.

@@

% ----------------------------------------------------------------------
\subsubsection{Fluctuating hydrodynamics}
\label{subsec:fluctuating}
Once algorithms that address quadrature, adaptive time stepping, and
contact are implemented, we will embark on incorporating fluctuating
hydrodynamics~\cite{Bao17,Bao18} which are important even at scales of
the some amphiphilic particles.

\todo[inline]{Using DLP formulation for fluctuating hydrodynamics so
that we have a second-kind BIE}
%\textcolor{red}{
%Once the collision-resolution algorithm is implemented, we will check
%the computing performance first before we embark on incorporating
%fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
%even at the scales of the amphiphilic particle size in some cases. We
%propose to extend the high-order time-integration scheme for a
%stochastic differential equation~\cite{fu2015pre} to this system.
%}
